Parsing Postfix log files

### 2007-12-04 doc/logparser-acronyms.tex
Added false positive/negative stuff to the coverage section.

\newacronym{pid}{Process IDentifier}{description={
    There may be multiple copies of any program executing at any one time,
    so the program's name is not suitable as a distinguishing identifier;
    instead each process executing is given a pid which is guaranteed to be
    unique for the lifetime of the process.  Once the process has
    completed, the pid may be reused, as they are drawn from a finite pool.
}}

@@

% I think this is better than having both regex and regexs in the acronym
% list.
\newcommand{\regexs}{\regex{}s}

>>>>

\newacronym{pid}{Process Identifier}{description={
    There may be multiple copies of any program executing at any one time,
    so the program's name is not suitable as a distinguishing identifier;
    instead each process executing is given a pid which is guaranteed to be
    unique for the lifetime of the process.  Once the process has
    completed, the pid may be reused, as they are drawn from a finite pool.
}}

@@

% I think this is better than having both regex and regexs in the acronym
% list.  Likewise for pids.
\newcommand{\regexs}{\regex{}s}
\newcommand{\pids}{\pid{}s}

### 2007-12-04 doc/logparser.tex
Added false positive/negative stuff to the coverage section.

XXX ADD SOMETHING ABOUT FALSE POSITIVES AND NEGATIVES\@.

@@

@@

The 13,850,793 connections and mails accepted, rejected or delivered by
Postfix during this period are handled correctly by the parser.

>>>>

@@

Warnings are issued for any lines which are not parsed; no warnings are
issued for unparsed lines while testing with the 93 test log files, so it
can be safely concluded that there are zero false negatives.  False
positives are harder to quantify: short of examining each of the 60,721,709
log lines and determining which \regex{} parsed it, there is no way to be
sure that every line was parsed by the correct \regex{}, making it
impossible to quantify the false positive rate.  The author is confident
that the false positive rate is extremely low, approaching if not reaching
zero, because the \regexs{} used are as specific as possible and care has
been taken to ensure that there are no unintentionally overlapping
\regexs{}.

@@

There are no mails in the state tables which should not be present, thus it
can be concluded that there are zero false negatives.  Once again,
determining the false positive rate is much harder, as manually checking
the results of parsing 13,850,793 connections and mails accepted, rejected,
bounced or delivered is infeasible.  There is considerable circumstantial
evidence that the false positive rate is quite low:

    \item The parser is quite verbose when complaining about known problems
        (e.g.\ if a mail is tracked twice as described in
        section~\refwithpage{tracking re-injected mail}), and no such
        warnings are produced during the test runs.

    \item Queueids and \pids{} naturally group together log lines belonging
        to one mail or connection, respectively; it is extremely unlikely
        that a log line would be associated with the wrong connection.

    \item When dealing with the complications described in
        sections~\refwithpage{complications} and~\refwithpage{additional
        complications} the solutions are as specific and restrictive as
        possible, with the goal of minimising the number of false
        positives.  In addition the solution to the \textit{Out of order
        log files\/} problem described in section~\refwithpage{out of order
        log lines} imposes conditions which each reassembled mail must
        comply with to be acceptable.

    \item Every effort has been made while developing to make the parser as
        precise, demanding and particular as possible.

Despite the lack of numerical evidence, the author is confident that the
false positive rate when reconstructing a mail is exceedingly low, if not
approaching zero.
